{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex

\section{Introduction} %%% 
\indent \indent Talk about the results and contributions concretely.
As short as possible summary of UX sprint here. %only what is necessary to understand results. 
Talk about the changes resulted in the Tor browser here.
As short as possible summary of lessons learned, 
and also a short as possible motivation for censorship work here. %yep, same.
Talk about the experiment design quickly here.

@@

\subsection{Censorship} %%%
\indent \indent Motivational paragraph time about how this is so everywhere.

\subsection{What is Required of Users}
\indent \indent For users to circumvent censorship in their resident countries, they will need to 
configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
have been blocked by the government. There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide IP addresses of proxies or bridges to use.

>>>>

\section{Introduction} %%% 
% \indent \indent Talk about the results and contributions concretely.
% As short as possible summary of UX sprint here. %only what is necessary to understand results. 
% Talk about the changes resulted in the Tor browser here.
% As short as possible summary of lessons learned, 
% and also a short as possible motivation for censorship work here. %yep, same.
% Talk about the experiment design quickly here.

We aim to improve user security by evaluating
and improving the usability of security software.
Both ``usability'' and ``security'' encompass many topics;
therefore we limit our scope and focus on
an important and timely use case:
user configuration of software to evade Internet censorship.
In this report, we detail the design of a usability-focused user experiment,
which we hope will be a benchmark for such studies
and guide their development in the future.

We hold that usability must be regarded as a security property.
It should be part of the design of security software.
Usable software not only decreases the risk of making mistakes
with dangerous security consequences,
but also provides a bridge over which users can
transition from substitutes that are less safe.

\subsection{Censorship} %%%
% \indent \indent Motivational paragraph time about how this is so everywhere.

@@

\subsection{What is Required of Users} %%%
\indent \indent For users to circumvent censorship in their resident countries, they will need to 
configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
have been blocked by the government. There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide IP addresses of proxies or bridges to use.
